Evaluation of +S2 sea ice forecast and some other better title

### 2025-02-24 analysis/paper/access-ice.qmd
udaptes error metrics

```{r errors}
errors <- rbind(
  readRDS(here::here("data/derived/rmse.Rds")) |>
    _[version != "S1"], 
  readRDS(here::here("data/derived/iiee.Rds"))
) |>
  _[value < 0.01, value := NA] |> 
  _[value > 3e13, value := NA] |> 
  _[, time := as.Date(time)] |> 
  _[, lag := as.numeric(time - time_forecast)] |> 
  _[lag > 0] |> 
  _[!(month(time_forecast) == 1 & member == "07" & version == "S1")]  # This member is wrong

@@

>>>>

```{r errors}
errors <- rbind(
  readRDS(here::here("data/derived/rmse.Rds")),
  readRDS(here::here("data/derived/iiee.Rds"))
) |> 
  _[value < 0.01, value := NA] |> 
  _[value > 3e13, value := NA] |> 
  _[, time := as.Date(time)] |> 
  _[, lag := as.numeric(time - time_forecast)] |> 
  _[lag > 0] |> 
  _[!(month(time_forecast) == 1 & member == "07" & version == "S1")]  # This member is wrong

@@

::: notes

Use climatology

monthly rmse/corelation at gridpoints per lead time.

:::
